The Perils of Exploration under Competition: \\ A Computational Modeling Approach

### 2020-09-05 journal paper/ec19paper/content/perf_in_iso.tex
Removed some coloring.

We start with a pilot experiment in which we investigate each algorithm's performance ``in isolation": in a stand-alone MAB problem without competition. We focus on reputation scores generated by each algorithm. We confirm that algorithms' performance is ordered as we'd expect:
    $\Thompson > \DynamicEpsGreedy > \DynamicGreedy$
for a sufficiently long time horizon. For each algorithm and each MAB instance, we compute the mean reputation score at each round, averaged over all \MRVs. We plot the \emph{mean reputation trajectory}: how this score evolves over time. \asedit{We also plot the trajectory for instantaneous rewards (\emph{not} averaged over the previous time-periods), which provides a better view into algorithm's performance at a given time.}%
\footnote{For ``instantaneous reward" at a given time $t$, we report the average (over all \MRVs) of the mean rewards at this time, instead of the average of the \emph{realized} rewards, so as to decrease the noise.}
Figure \ref{prelim_means} shows these trajectories for the Needle-in-Haystack instance; for other MAB instances the plots are similar.

@@

\begin{finding}
\textit{The mean reputation trajectories \asedit{and the instantaneous reward trajectories} are arranged as predicted by prior work:
    $\Thompson > \DynamicEpsGreedy > \DynamicGreedy$ for a sufficiently long time horizon $T$.}
\end{finding}

>>>>

We start with a pilot experiment in which we investigate each algorithm's performance ``in isolation": in a stand-alone MAB problem without competition. We focus on reputation scores generated by each algorithm. We confirm that algorithms' performance is ordered as we'd expect:
    $\Thompson > \DynamicEpsGreedy > \DynamicGreedy$
for a sufficiently long time horizon. For each algorithm and each MAB instance, we compute the mean reputation score at each round, averaged over all \MRVs. We plot the \emph{mean reputation trajectory}: how this score evolves over time. We also plot the trajectory for instantaneous rewards (\emph{not} averaged over the previous time-periods), which provides a better view into algorithm's performance at a given time.%
\footnote{For ``instantaneous reward" at a given time $t$, we report the average (over all \MRVs) of the mean rewards at this time, instead of the average of the \emph{realized} rewards, so as to decrease the noise.}
Figure \ref{prelim_means} shows these trajectories for the Needle-in-Haystack instance; for other MAB instances the plots are similar.

@@

\begin{finding}
\textit{The mean reputation trajectories and the instantaneous reward trajectories are arranged as predicted by prior work:
    $\Thompson > \DynamicEpsGreedy > \DynamicGreedy$ for a sufficiently long time horizon $T$.}
\end{finding}
